### 2015-08-10 chapters/introduction.tex
added EHT section

\section{The Event Horizon Telescope}

@@

\section{Thesis Outline}

>>>>

V4046 Sgr is a system with two stars closely orbiting each other.  Around this tight binary is a bright
protoplanetary disk.  In chapter \ref{chap:V4046Sgr} we present Submillimimeter Array (SMA) observations of this 
disk 
that resolve for the
first time a large central cavity.  In addition, we show that the distribution of gas and dust are non-commitant 
with each other: the gas disk is large and extended while the mm-sized dust grains are concentrated in a narrow 
ring.  Furthermore, we show that dust within ring is not completely cleared.  We argue that this configuration is 
the hallmark of old disk sculpted by at least one large, embedded planet.  HD163296 also has a very large, bright gaseous disk, but no resolved cavity.  In chapter \ref{chap:hd163296} we 
use 
science verification data from the Atacama Large Millimimeter Array (ALMA) to study the vertical structure of 
this disk.  We argue that resolved features in the images highlight how the temperature of the gas changes with
its distance from mid-plane and explore additional, nuanced aspects of the disk structure and how they may 
affect the observables.   In chapter \ref{chap:radial_flows} we consider what impact radial motions of gas within transition disk 
holes may have upon spectral line emission.  We discuss several indicators of such radial flows along 
with possible sources of confusion such as warps in the disk.

@@

\section{Sample Rate Conversion for the EHT}

The Event Horizon Telescope (EHT) uses VLBI to observe supermassive black holes, obtaining resolution high enough
to resolve event horizon scales of nearby targets.  These observations provide a 
unique glimpse into one of the most extreme environments in our universe.  Using telescopes in Hawaii, Arizona, 
and California, the collaboration has already detected structure at these scales for Sgr A$^\ast$ in the galactic 
center and the giant elliptical galaxy M87 \citep{doeleman08,doeleman09}.  These data have provided indirect 
evidence for existence of an event horizon \citep{broderick15} along with constraints on the degree of 
magnetization in the jet of M87 \citep{kino15} and the orientation of Sgr A$^\ast$ \citep{broderick11}.  EHT 
observations promise to provide tests of general relativity \citep{luminet79,johannsen10,bambi13,broderick14} as 
well as new studies of black hole time variability \citep{doeleman09} and black hole accretion \citep{chan15}.

The bright future of the EHT rests on its key ability to expand by adding more telescopes and
incorporating new technologies into its operations.  The March 2015 observing campaign was a major milestone in
the EHT expansion with participation from the LMT in Mexico, CARMA in California, the SMA and JCMT in Hawaii, 
SMT in Arizona and 30m at Pico Valeta in Spain.  However, the data taken at the SMA must be processed before it
can be correlated with the rest of the array.  In chapter \ref{chap:aphids} we describe the \APHIDS\, pipeline
which performs a sampling rate conversion using a cluster of Graphcs Processing Units (GPUs).  This software
is intended to be a long-term solution to enable VLBI with the SMA and has applications for other sites such 
as ALMA that operate at a sampling rate that is not compatible with the standard VLBI data product.
